Contracts for unions and intersections are hard for Nickel

### 2021-05-11 paper.tex
Started the zoology

\section*{Introduction}
Intro\unsure{todo}
\info{Goals of the paper: position paper: unions/intersections nice in
theory problematic in practice. In particular non-orthogonal with the
rest of the features of your language.}

@@

>>>>

\section{Introduction}
Intro\unsure{todo}
\info{Goals of the paper: position paper: unions/intersections nice in
theory problematic in practice. In particular non-orthogonal with the
rest of the features of your language.}

@@

Programming language research no longer lives on the abstract world
of ideal surfaces.
Every addition needs to be compatible with years of research
and development, and this is hard.
Success was unavoidable.

In this section we briefly introduce some aspects of real world
programming languages that will cause trouble while interacting
with union and intersection dynamic checks.

\subsection*{User defined (flat) contracts}

User defined contracts, also called flat contracts, are a particular
kind of contract that behaves similar to an assertion, and whose
main point is to apply some arbitrary predicate (as arbitrary as the
host language allows it) to a value; if the predicate returns true,
the contract passes, otherwise it fails.

For instance, we could define a flat contract $even?$ as 
$\lambda x. ~ x ~ \% ~ 2 ~ == ~ 0$, that checks
whether a number is even.
And then use it to check that a function always returns an
even number, for example:

$$let~f~=~(\lambda n. ~ n * 2)@Number ~ \rightarrow ~ even?$$

\unsure{Do we need deeper examples?}

This kind of contracts are present on many different languages,
for instance, the Eiffel programming language, the precursor
on the Design by Contract ideals, allows to assert
exactly these kinds of expression as pre- and post-conditions on
functions.

The Racket programming language also has a system to work with
contracts\footnote{And a gradual typing system
built on top of that, but that goes beyond the scope of this
work.} that provides a mechanism for defining them; and
composing these with other kinds of constructs.

Even if flat contracts may seem like too much, these are expected
by programmers on dynamic languages, where testing and runtime
assertions are a common pattern for safe programming, and 
programmers are used to express complex predicates
over values.

\subsection*{Code manipulation (optimizations)}
\info{Present inlining and CSE as two major code
optimizations.
Purity and immutability as two important factors.}
